%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\cvsubsection{Research}

\begin{cventries}
%------------------------------------------------
\cventry
{Graduate Research Assistant} % Job title
{Georgia Institute of Technology {\normalfont ~|~ School of Biological Sciences} {\normalfont ~|~ \href{http://jordan.biology.gatech.edu}{Jordan Lab}}} % Organization
{Atlanta, USA} % Location
{2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
% \vspace{2.0mm}
\textit{\normalfont{\color{graytext}Efficient Alignment-free Software Applications for NGS-based Molecular Epidemiology}}
\vspace{\acvDescAfterDutiesSkip}
\begin{cvitems}
\item {Developed an alignment-free software based on \textit{k}-mer frequencies for sequence typing directly from raw sequencing reads.}
\item {Extended the \textit{k}-mer approach to develop an alignment-free application for gene detection from raw sequencing reads.}
\item {Developed a Web-accessible interface for sequence typing and phenotypic characterization of WGS samples. In colaboration with the Applied Bioinformatics Laboratory Inc., IHRC Inc., and Weems Design Studio.}
\item {Developing an alignment-free software for \textit{nifH} gene-based taxonomy assignment of amplicon sequencing samples.}
\end{cvitems}
}

\vspace{\acvSectionContentTopSkip}
%------------------------------------------------
\cventry
{Graduate Research Assistant} % Job title
{Colombian Sugarcane Research Center (CENICAÑA) and Universidad del Valle} % Organization
{Cali, Colombia} % Location
{2012 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
% Advisor: Dr. John Riascos; Co-advisor: Dr. Irene Tischer\newline
% \vspace{2.0mm}
% \textit{\normalfont{\color{graytext}General Bioinformatics Reasearch}}
% \vspace{\acvDescAfterDutiesSkip}
\begin{cvitems}
    \item {Established a bioinformatics platform for the sugarcane applied research.}
    \item {Developed pipelines for sugarcane RNA-seq transcriptome assembly, and identification of sugarcane variants related to agronomic traits of interest from RAD-seq and GBS data.}
% \end{cvitems}
% \vspace{6.0mm}
% \textit{\normalfont{\color{graytext}Development of a Data Mining Model for Identifying Sugarcane Candidate Genes Related to Drought and Flooding Tolerance}}
% \vspace{\acvDescAfterDutiesSkip}
% \begin{cvitems}
    \item {Studied gene expression in sugarcane under water stress (drought and flooding) using RNA-seq analysis.}
    \item {Developed a framework for identifying sugarcane cDNAs related to water-stress tolerance, using RNA-seq expression analysis, co-expression network analysis, and machine learning.}
    % \item{Studied differential expression of sugarcane cDNAs related to drought and flooding tolerance.}
    % \item{Selected candidate sugarcane cDNAs involved in biological processes related to drought and flooding tolerance using co-expression network analysis, and machine learning feature selection.}
    % \item{Deployed and maintained a Galaxy server instance for custom RNA-seq analysis pipelines.}
\end{cvitems}
\vspace{\acvDescAfterDutiesSkip}
% \textit{Languages used:~ R, Bash, Perl, Python, awk, HTML, CSS, Javascript}
}
\end{cventries}

\vspace{\acvSectionContentTopSkip}
%------------------------------------------------
\cventry
{Undergraduate Research Assistant} % Job title
{Universidad del Valle {\normalfont ~|~ Bioinformatics and Biocomputing Research Group}} % Organization
{Cali, Colombia} % Location
{2009 - 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
% Advisor: Dr. Pedro Moreno; Co-advisor: Dr. Irene Tischer\newline
% \vspace{2.0mm}
% \textit{\normalfont{\color{graytext}Development of an Application for Multifractal Analysis on DNA and Protein Sequences using the Sand-box Method}}
% \vspace{\acvDescAfterDutiesSkip}
\begin{cvitems}
\item {Developed a software application for multifractal analysis on complete genomes.}
\end{cvitems}
% \vspace{\acvDescAfterDutiesSkip}
% \textit{Languages/tools used:~ C++, Python, UML}
}
% \vspace{\acvSectionContentTopSkip}

%------------------------------------------------
\cvsubsection{Software Development}

\begin{cventries}
%------------------------------------------------
\cventry
{Junior Software Development Engineer} % Job title
{Universidad del Valle {\normalfont ~|~ Informatics and Telecommunications Office}} % Organization
{Cali, Colombia} % Location
{2011 - 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Analyzed, designed and implemented software for an integrated Web-based management system for the Universidad del Valle.}
\end{cvitems}
% \vspace{\acvDescAfterDutiesSkip}
% \textit{Languages/tools used:~ UML, PHP (Symfony framework), HTML}
}
%------------------------------------------------
\end{cventries}

% \vspace{\acvSectionContentTopSkip}
%------------------------------------------------
\cvsubsection{Teaching}

\begin{cventries}

%------------------------------------------------
\cventry
{Adjunct Professor} % Job title
{Universidad del Valle} % Organization
{Palmira, Colombia} % Location
{2010 - 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
% Courses:\newline
% \vspace{\acvDescAfterDutiesSkip}
\begin{cvitems}
\item {Taught and administrated classes in engineering undergraduate programs.}
% \item {Algorithms and Programming}
% \item {Introduction to Computer Technology}
% \item {Systems General Theory}
\end{cvitems}
\vspace{\acvDescAfterDutiesSkip}
\textit{Courses taught:~ Algorithms and Programming, Systems General Theory, and Introduction to Computer Technology}
}
% \vspace{\acvSectionTopSkip}
%------------------------------------------------

\end{cventries}